Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-10-04 prop_letter.tex
prop_letter.tex \section{Gleason} Discussing norm...

Nielsen and Chuang~\citep{544199} defined their norm~(\ref{eq:norm})
in Appendix~6

Although Nielsen and Chuang~\citep{544199} in Appendix 6 follow
Simon {[}2{]} to prove theorems, it seems Simon didn't define the
norm in his book {[}2{]}, and the definition used in Nielsen and Chuang
{[}1{]} is clearly not what Simon would like to use... Figuring out
what we should use...

>>>>

Nielsen and Chuang~\citep{544199} defined their norm~(\ref{eq:norm})
in Appendix~6. While their Appendix~6 followed Simon~\citep{Simon2005}
and Uhlmann~\citep{Uhlmann1977} to prove Lieb's theorem~\citep{Lieb_1973,544199,Simon2005},
Simon~\citep{Simon2005} and Uhlmann~\citep{Uhlmann1977} didn't
explicitly define the norm as in Eq.~(\ref{eq:norm}) although Simon
used the same norm thoroughly in his book~\citep{Simon2005}. There
are two possibilities:
\begin{enumerate}
\item Simon really used Eq.~(\ref{eq:norm}) to define his norm.\\
If this is true, there must be some books cited by Simon, and defined
the norm in the same way.
\item The norm Simon used is different from Eq.~(\ref{eq:norm}), and Nielsen
and Chuang defined this norm from nowhere in order to write a proof
of Lieb's theorem.\\
If this is true, Nielsen and Chuang might be the \emph{only} literature
which used this norm. We might have no other literature to check the
properties of this norm and other distances, and need to prove the
properties of this norm by ourselves.
\end{enumerate}
In order to understand this norm and compare with others, the following
are useful facts.
